Ice sheet mass flows

### 2024-06-22 sankey.tex
Labels

  \begin{sankeydiagram}
    \sankeyset{debug=true}

@@

    \sankeyset{
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/33,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-water-horiz/.style={fill/.style={fill=none, right color=ice, left color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-air-horiz/.style={fill/.style={fill=none, left color=ice, right color=air},},
      water-to-air-horiz/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

@@

@@

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG},
        at={[xshift=\xoff,yshift=8mm]SUa.left}, anchor=right, angle=0}
      \sankeyoutin{MG}{MGa}
    \fi

@@

    \ifthenelse{\Q{vMG} < \Q{vML}}
      {
        %% mass loss
        \sankeynode{name=ML, quantity=\Q{vML},
          at={[xshift=-\xoff]RF.right}, anchor=left} %, angle=-45}
        \sankeystart[red]{ML}
        \sankeyadvance[red-to-ice]{ML}{5mm}
        \sankeyoutin{ML}{MLi}
      }
      {
        %% mass gain
        \sankeyadvance[ice-to-black]{MGa}{3mm}
        \sankeyend[black]{MGa}
      }

@@

>>>>

  \begin{sankeydiagram}
    %% \sankeyset{debug=true}

@@

    \sankeyset{
      %% comment for gray outline
      draw/.style={
        draw=white,
        line width=0pt,line cap=round,line join=round,
      },
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/33,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-water-horiz/.style={fill/.style={fill=none, right color=ice, left color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-air-horiz/.style={fill/.style={fill=none, left color=ice, right color=air},},
      water-to-air-horiz/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

    \newcommand\abovelabel[2]{ % valname, label
      \node[font=\tiny, rotate=45, anchor=north west]
      at ([yshift=5mm,xshift=-3mm]#1.center) {\qq{#1}: #2};
    }
    \newcommand\belowlabel[2]{ % valname, label
      \node[font=\tiny, rotate=-45, anchor=south west]
      at ([yshift=-6mm,xshift=-3mm]#1.center) {\qq{#1}: #2};
    }

@@

    \abovelabel{SF}{Snowfall}
    \abovelabel{DP}{Deposition}
    \abovelabel{CD}{Condensation}
    \abovelabel{RF}{Rainfall}

@@

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG},
        at={[xshift=\xoff,yshift=8mm]SUa.left}, anchor=right, angle=0}

      \node[font=\tiny, anchor=north]
      at ([yshift=-5mm,xshift=9mm]MGa.bottom) {\qq{MGa}: Accumulation};

      \sankeyoutin{MG}{MGa}
    \fi

@@

    \ifthenelse{\Q{vMG} < \Q{vML}}
      {
        %% mass loss
        \sankeynode{name=ML, quantity=\Q{vML},
          at={[xshift=-\xoff]RF.right}, anchor=left} %, angle=-45}
        \abovelabel{ML}{Drawdown}
        \sankeystart[red]{ML}
        \sankeyadvance[red-to-ice]{ML}{5mm}
        \sankeyoutin{ML}{MLi}
      }
      {
        %% mass gain
        \sankeyadvance[ice-to-black]{MGa}{3mm}
        \sankeyend[black]{MGa}
      }

@@

      \belowlabel{RU}{Runoff}
      \belowlabel{BMa}{Basal melting}
      \belowlabel{SUBa}{Submarine melting}
      \belowlabel{D}{Discharge}
      \belowlabel{GZa}{Grounding line retreat}
      \belowlabel{FRa}{Frontal retreat}

      \node[font=\tiny, anchor=north]
      at ([yshift=-2mm,xshift=3mm]SUaa.bottom) {\qq{SUa}: Sublimation};

      \node[font=\tiny, anchor=north]
      at ([yshift=-2mm,xshift=0mm]EVa.bottom) {\qq{EVa}: Evaporation};

      \node[font=\tiny, anchor=west, rotate=-90]
      at ([yshift=0.5mm,xshift=1mm]RFZi.center) {\qq{RFZi}: Refreezing};
